Bayesian Nonparametric System Reliability\\ using Sets of Priors

### 2016-07-05 ijar-npb-ms.tex
final tweaks

Furthermore, with sets of Beta priors it is also possible
to express prior ignorance
by letting $\yktzl \to 0$ and $\yktzu \to 1$
for some or all $t \in {\cal T}$.
Such models are called \emph{near-noninformative} or \emph{near-ignorance models} in the imprecise probability literature
(see \citet[\S5.3.2]{1991:walley} for Beta priors,
and \citet{2012:benavolizaffalon,2015:benavolizaffalon} for exponential family priors),
as they provide vacuous bounds only for a certain class of inferences,
and the choice for the prior strength parameter $\nktz$ influences posterior inferences.
(Note that it is not advisable to choose $\yktzl = 0$ and $\yktzu = 1$,
as this can lead to improper posterior predictive distributions.
For example, at any $t < \min(\vec{t}^k)$,
we would have $\yktnu = 1$, leading to one argument of the Beta function
in the denominator of \eqref{eq:postpredCny} being zero.)
The limits $\yktzl \to 0$ and $\yktzu \to 1$ imply we are only prepared to give trivial bounds for the functioning probability
and do not wish to commit to any specific knowledge about $p^k_t$ \emph{a priori}.
This provides a more natural choice of `noninformative' prior over $[0,1]$ than the usual choice of
a Beta prior with $\alpha^k_t = \beta^k_t = 1$ (or $\nktz = 2$, $\yktz = 0.5$).
Such a prior for all $t \in {\cal T}$ actually reflects a belief that the component reliability function
is on average 1/2 for all $t$, which is not an expression of ignorance, but rather a very specific (and arguably peculiar) prior belief.

>>>>

Furthermore, with sets of Beta priors it is also possible
to express prior ignorance
by letting $\yktzl \to 0$ and $\yktzu \to 1$
for some or all $t \in {\cal T}$.
Such models are called \emph{near-noninformative} or \emph{near-ignorance models} in the imprecise probability literature
(see \citet[\S5.3.2]{1991:walley} for Beta priors,
\cite{1996:walley::IDM} for Dirichlet priors,
and \citet{2012:benavolizaffalon,2015:benavolizaffalon} for exponential family priors),
as they provide vacuous bounds only for a certain class of inferences,
and the choice for the prior strength parameter $\nktz$ influences posterior inferences.
(Note that it is not advisable to choose $\yktzl = 0$ and $\yktzu = 1$,
as this can lead to improper posterior predictive distributions.
For example, at any $t < \min(\vec{t}^k)$,
we would have $\yktnu = 1$, leading to one argument of the Beta function
in the denominator of \eqref{eq:postpredCny} being zero.)
The limits $\yktzl \to 0$ and $\yktzu \to 1$ imply we are only prepared to give trivial bounds for the functioning probability
and do not wish to commit to any specific knowledge about $p^k_t$ \emph{a priori}.
This provides a more natural choice of `noninformative' prior over $[0,1]$ than the usual choice of
a Beta prior with $\alpha^k_t = \beta^k_t = 1$ (or $\nktz = 2$, $\yktz = 0.5$).
Such a prior for all $t \in {\cal T}$ actually reflects a belief that the component reliability function
is on average 1/2 for all $t$, which is not an expression of ignorance, but rather a very specific (and arguably peculiar) prior belief.
